2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal

### 2023-07-21 paperCharts.Rmd
first submission

---
title: "2040 greenhouse gas reduction targets"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

@@

Rodrigues, R., Pietzcker, R., Luderer, G., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A. M., Baumstark, L. 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal. in preparation (2023).

@@

electricity_share_in_FE <- data.frame(
  electricity_share_in_FE = c("2040"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
  ),
  min=c(
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  ),
  max=c(
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  )
)

@@

@@

@@

@@

@@

CDR <- data.frame(
  result=c("CCS_deployment_in_2030_MtCO2","CCS_deployment_in_2040_MtCO2","CCS_upscaling_rates_2030_2040_%","novel_CDR_upscaling_rates_2030_2040_%","novel_CDR_deployment_in_2040_MtCO2"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round((rateCCS %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round((rateCDR %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
  ),
  min = c(
    round(min(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((min(rateCCS %>% pull(rate))-1)*100),
    round((min(rateCDR %>% pull(rate))-1)*100),
    round(min(totalCDR %>% pull(value)))
  ),
  max = c(
    round(max(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((max(rateCCS %>% pull(rate))-1)*100),
    round((max(rateCDR %>% pull(rate))-1)*100),
    round(max(totalCDR %>% pull(value)))
  )
)

@@

@@

# Primary Energy
vars <- c("Biomass" = "PE|Biomass",
          "Coal"="PE|Coal",
          "Gas"="PE|Gas",
          "Oil"="PE|Oil")

>>>>

---
title: "2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

@@

Rodrigues, R., Pietzcker, R., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A. M., Baumstark, L., Luderer, G. 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal. under revision (2023).

@@

electricity_share_in_FE <- data.frame(
  electricity_share_in_FE = c("2030","2040"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100),
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
  ),
  min=c(
    round(min(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  ),
  max=c(
    round(max(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  )
)

@@

wind_and_Solar_participation <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario,period) %>%
  summarize(value = sum(value),.groups = "keep") %>%
  select(scenario,period,value)
  ,
  df %>%
  filter(region == "EU27", period == 2040, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
  mutate(total = value) %>%  
  select(scenario,period,total)
  , by = join_by(scenario == scenario,period == period)
) %>%
  mutate(pctg = value/total)

wind_and_Solar_participation <- data.frame(
  result=c("Wind_and_Solar_participation_2040_%"),
  reference_value=c(
    round((wind_and_Solar_participation %>% filter(scenario == mainScen) %>% pull(pctg))*100)
  ),
  min = c(
    round((min(wind_and_Solar_participation %>% pull(pctg)))*100)
  ),
  max = c(
    round((max(wind_and_Solar_participation %>% pull(pctg)))*100)
  )
)

@@

BEVs_in_LDV_data <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("Stock|Transport|LDV|BEV"), tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%    
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("Stock|Transport|LDV|BEV","Stock|Transport|LDV|FCEV","Stock|Transport|LDV|Hybrid Electric","Stock|Transport|LDV|Liquids","Stock|Transport|LDV|NG"), tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%  
  summarize(total = sum(value)) %>% 
  select(scenario,total)  
  ,
  by = join_by(scenario == scenario)
) %>% 
  mutate(pctg = value/total)

BEVs_in_LDV <- data.frame(
  FE=c("share_of_EVs_in_LDVs_(%)"),
  reference_value=c(round(BEVs_in_LDV_data %>% filter(scenario == mainScen) %>% pull(pctg)*100 )),
  min = c(round(min((BEVs_in_LDV_data %>% pull(pctg)) *100))),
  max = c(round(max((BEVs_in_LDV_data %>% pull(pctg)) *100)))
)

@@

wind_and_Solar_participation %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

BEVs_in_LDV %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

CDR <- data.frame(
  result=c("CCS_deployment_in_2030_MtCO2","CCS_deployment_in_2040_MtCO2","CCS_upscaling_rates_2030_2040_%","novel_CDR_upscaling_rates_2030_2040_%","novel_CDR_deployment_in_2040_MtCO2"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round((rateCCS %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round((rateCDR %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
  ),
  min = c(
    round(min(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((min(rateCCS %>% pull(rate))-1)*100),
    round((min(rateCDR %>% pull(rate))-1)*100),
    round(min(totalCDR %>% filter(period == 2040) %>% pull(value)))
  ),
  max = c(
    round(max(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((max(rateCCS %>% pull(rate))-1)*100),
    round((max(rateCDR %>% pull(rate))-1)*100),
    round(max(totalCDR %>% filter(period == 2040) %>% pull(value)))
  )
)

@@

## Milestones upscaling rates

# Final Energy
FEbySector <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable %in% c("FE|Transport","FE|Buildings","FE|Industry"), tgt2030 %in% tgt2030Scen) %>%
    mutate(end=value) %>%
    select(variable,scenario,end)
  ,
  df %>%
    filter(region == "EU27", period == 2020, variable %in% c("FE|Transport","FE|Buildings","FE|Industry"), tgt2030 %in% tgt2030Scen) %>%
    mutate(base=value) %>%
    select(variable,scenario,base)
  , by = join_by(scenario == scenario, variable == variable)
) %>%
  mutate(percentage = (end-base)/base)

FEbySector_change <- data.frame(
  result=c("FE_Transport_change_%","FE_Buildings_change_%","FE_Industry_change_%"),
  reference_value=c(
    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Transport") %>% pull(percentage))*100),
    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Buildings") %>% pull(percentage))*100),
    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Industry") %>% pull(percentage))*100)
  ),
  min = c(
    round((min(FEbySector %>% filter(variable == "FE|Transport") %>% pull(percentage)))*100),
    round((min(FEbySector %>% filter(variable == "FE|Buildings") %>% pull(percentage)))*100),
    round((min(FEbySector %>% filter(variable == "FE|Industry") %>% pull(percentage)))*100)
  ),
  max = c(
    round((max(FEbySector %>% filter(variable == "FE|Transport") %>% pull(percentage)))*100),
    round((max(FEbySector %>% filter(variable == "FE|Buildings") %>% pull(percentage)))*100),
    round((max(FEbySector %>% filter(variable == "FE|Industry") %>% pull(percentage)))*100)
  )
)

# Renewables Share in Final Energy
rate2030_2040RenewablesShare <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

rate2021_2030RenewablesShare <- 
  df %>%
    filter(region == "EU27", period == 2030, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value)) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/9))

renewablesShare <- data.frame(
  result=c("Renewables_Share_upscaling_rates_2021_to_2030_%","Renewables_Share_upscaling_rates_2030_to_2040_%"),
  reference_value=c(
    round((rate2021_2030RenewablesShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2030_2040RenewablesShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2021_2030RenewablesShare %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040RenewablesShare %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2021_2030RenewablesShare %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040RenewablesShare %>% pull(rate))-1)*100,1)
  )
)

# Electricity Share in Final Energy
rate2030_2040ElectricityShare <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share","Final Energy|Transport|Electricity Share","Final Energy|Industry|Electricity Share","Final Energy|Buildings|Electricity Share"), tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(variable,scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share","Final Energy|Transport|Electricity Share","Final Energy|Industry|Electricity Share","Final Energy|Buildings|Electricity Share"), tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(variable,scenario,denominator)
  , by = join_by(scenario == scenario, variable == variable)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

#estimation of historical share in 2021 for FE electricity / FE with non-energy use and with bunkers
h <- (
      2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
     ) / (
      addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2021) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
     )

rate2021_2030ElectricityShare <- 
  df %>%
    filter(region == "EU27", period == 2030, variable == "Final Energy|Electricity Share", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=h) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/9))

ElectricityShare <- data.frame(
  result=c("Electricity_Share_upscaling_rates_2021_to_2030_%","Electricity_Share_upscaling_rates_2030_to_2040_%","Transport_Electricity_Share_upscaling_rates_2030_to_2040_%","Buildings_Electricity_Share_upscaling_rates_2030_to_2040_%","Industry_Electricity_Share_upscaling_rates_2030_to_2040_%"),
  reference_value=c(
    round((rate2021_2030ElectricityShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Electricity Share") %>% pull(rate)-1)*100,1),
    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Transport|Electricity Share") %>% pull(rate)-1)*100,1),
    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate)-1)*100,1),
    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Industry|Electricity Share") %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2021_2030ElectricityShare %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Electricity Share") %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Transport|Electricity Share") %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Industry|Electricity Share") %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2021_2030ElectricityShare %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Electricity Share") %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Transport|Electricity Share") %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Industry|Electricity Share") %>% pull(rate))-1)*100,1)
  )
)

# Hydrogen production
rate2030_2040hydrogenProduction <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

rate2040_2050hydrogenProduction <- left_join(
  df %>%
    filter(region == "EU27", period == 2050, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2040, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

hydrogenProduction <- data.frame(
  result=c("Hydrogen_upscaling_rates_2030_to_2040_%","Hydrogen_upscaling_rates_2040_to_2050_%"),
  reference_value=c(
    round((rate2030_2040hydrogenProduction %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2040_2050hydrogenProduction %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2030_2040hydrogenProduction %>% pull(rate))-1)*100,1),
    round((min(rate2040_2050hydrogenProduction %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2030_2040hydrogenProduction %>% pull(rate))-1)*100,1),
    round((max(rate2040_2050hydrogenProduction %>% pull(rate))-1)*100,1)
  )
)

# Electricity Demand
rate2030_2040ElectricityDemand <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator = value * 1/0.0036) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator = value * 1/0.0036) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(diff = (numerator - denominator)/10,
         percentage = numerator/denominator,
         rate = percentage ^ (1/10))

#2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
h <- 2469471.42 /1000

rate2022_2030ElectricityDemand <- 
  df %>%
    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator = value * 1/0.0036) %>%
    select(scenario,numerator) %>%
    mutate(denominator=h) %>%
    mutate(diff = (numerator - denominator)/8,
           percentage = numerator/denominator,
           rate = percentage ^ (1/8))

rate2020_2030ElectricityDemand <- left_join(
  df %>%
    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator = value * 1/0.0036) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2020, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator = value * 1/0.0036) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(diff = (numerator - denominator)/10,
         percentage = numerator/denominator,
         rate = percentage ^ (1/10))

ElectricityDemand <- data.frame(
  result=c("Electricity_Demand_yearly_install_2022_to_2030_(Twh)","Electricity_Demand_yearly_install_2030_to_2040_(Twh)","Electricity_Demand_upscaling_rates_2022_to_2030_%","Electricity_Demand_upscaling_rates_2020_to_2030_%","Electricity_Demand_upscaling_rates_2030_to_2040_%"),
  reference_value=c(
    round(rate2022_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(diff)),
    round(rate2030_2040ElectricityDemand %>% filter(scenario == mainScen) %>% pull(diff)),
    round((rate2022_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2020_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2030_2040ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2022_2030ElectricityDemand %>% pull(diff)))),
    round((min(rate2030_2040ElectricityDemand %>% pull(diff)))),
    round((min(rate2022_2030ElectricityDemand %>% pull(rate))-1)*100,1),
    round((min(rate2020_2030ElectricityDemand %>% pull(rate))-1)*100,1),
    round((min(rate2030_2040ElectricityDemand %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2022_2030ElectricityDemand %>% pull(diff)))),
    round((max(rate2030_2040ElectricityDemand %>% pull(diff)))),
    round((max(rate2022_2030ElectricityDemand %>% pull(rate))-1)*100,1),
    round((max(rate2020_2030ElectricityDemand %>% pull(rate))-1)*100,1),
    round((max(rate2030_2040ElectricityDemand %>% pull(rate))-1)*100,1)
  )
)

# # Electricity Supply
# rate2030_2040ElectricitySupply <- left_join(
#   df %>%
#     filter(region == "EU27", period == 2040, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
#     mutate(numerator = value * 1/0.0036) %>%
#     select(scenario,numerator)
#   ,
#   df %>%
#     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
#     mutate(denominator = value * 1/0.0036) %>%
#     select(scenario,denominator)
#   , by = join_by(scenario == scenario)
# ) %>%
#   mutate(percentage = numerator/denominator,
#          rate = percentage ^ (1/10))
# 
# rate2020_2030ElectricitySupply <- left_join(
#   df %>%
#     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
#     mutate(numerator = value * 1/0.0036) %>%
#     select(scenario,numerator)
#   ,
#   df %>%
#     filter(region == "EU27", period == 2020, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
#     mutate(denominator = value * 1/0.0036) %>%
#     select(scenario,denominator)
#   , by = join_by(scenario == scenario)
# ) %>%
#   mutate(percentage = numerator/denominator,
#          rate = percentage ^ (1/10))
# 
# # #2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
# # h <- 2469471.42 /1000
# # 
# # rate2022_2030ElectricitySupply <- 
# #   df %>%
# #     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
# #     mutate(numerator = value * 1/0.0036) %>%
# #     select(scenario,numerator) %>%
# #     mutate(denominator=h) %>%
# #     mutate(percentage = numerator/denominator,
# #            rate = percentage ^ (1/8))
# 
# ElectricitySupply <- data.frame(
#   result=c("Electricity_Supply_upscaling_rates_2022_to_2030_%","Electricity_Supply_upscaling_rates_2030_to_2040_%"),
#   reference_value=c(
#     round((rate2022_2030ElectricitySupply %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
#     round((rate2030_2040ElectricitySupply %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
#   ),
#   min = c(
#     round((min(rate2022_2030ElectricitySupply %>% pull(rate))-1)*100,1),
#     round((min(rate2030_2040ElectricitySupply %>% pull(rate))-1)*100,1)
#   ),
#   max = c(
#     round((max(rate2022_2030ElectricitySupply %>% pull(rate))-1)*100,1),
#     round((max(rate2030_2040ElectricitySupply %>% pull(rate))-1)*100,1)
#   )
# )

# Solar Photovoltaics
rate2030_2040SolarPV <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

rate2022_2030SolarPV <- 
  df %>%
    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=208.9) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/8))

rate2022_2040SolarPV <- 
  df %>%
    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=208.9) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/18))

SolarPV <- data.frame(
  result=c("SolarPV_2022_vs_2040_X", "SolarPV_upscaling_rates_2030_to_2040_%","SolarPV_upscaling_rates_2022_to_2040_%","SolarPV_upscaling_rates_2022_to_2030_%"),
  reference_value=c(
    round((rate2022_2040SolarPV %>% filter(scenario == mainScen) %>% pull(percentage)),1),
    round((rate2030_2040SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2022_2040SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2022_2030SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2022_2040SolarPV %>% pull(percentage))),1),
    round((min(rate2030_2040SolarPV %>% pull(rate))-1)*100,1),
    round((min(rate2022_2040SolarPV %>% pull(rate))-1)*100,1),
    round((min(rate2022_2030SolarPV %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2022_2040SolarPV %>% pull(percentage))),1),
    round((max(rate2030_2040SolarPV %>% pull(rate))-1)*100,1),
    round((max(rate2022_2040SolarPV %>% pull(rate))-1)*100,1),
    round((max(rate2022_2030SolarPV %>% pull(rate))-1)*100,1)
  )
)

# Wind
rate2030_2040Wind <- left_join(
  df %>%
    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator)
  ,
  df %>%
    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
    mutate(denominator=value) %>%
    select(scenario,denominator)
  , by = join_by(scenario == scenario)
) %>%
  mutate(percentage = numerator/denominator,
         rate = percentage ^ (1/10))

rate2022_2030Wind <- 
  df %>%
    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=255) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/8))

rate2022_2040Wind <- 
  df %>%
    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
    mutate(numerator=value) %>%
    select(scenario,numerator) %>%
    mutate(denominator=255) %>%
    mutate(percentage = numerator/denominator,
           rate = percentage ^ (1/18))

Wind <- data.frame(
  result=c("wind_2022_vs_2040_X","Wind_upscaling_rates_2030_to_2040_%","Wind_upscaling_rates_2022_to_2040_%","Wind_upscaling_rates_2022_to_2030_%"),
  reference_value=c(
    round((rate2022_2040Wind %>% filter(scenario == mainScen) %>% pull(percentage)),1),
    round((rate2030_2040Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2022_2040Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
    round((rate2022_2030Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
  ),
  min = c(
    round((min(rate2022_2040Wind %>% pull(percentage))),1),
    round((min(rate2030_2040Wind %>% pull(rate))-1)*100,1),
    round((min(rate2022_2040Wind %>% pull(rate))-1)*100,1),
    round((min(rate2022_2030Wind %>% pull(rate))-1)*100,1)
  ),
  max = c(
    round((max(rate2022_2040Wind %>% pull(percentage))),1),
    round((max(rate2030_2040Wind %>% pull(rate))-1)*100,1),
    round((max(rate2022_2040Wind %>% pull(rate))-1)*100,1),
    round((max(rate2022_2030Wind %>% pull(rate))-1)*100,1)
  )
)

#residual fossils
residualFossils <- data.frame(
  result=c("residual_fossil_MtCO2_2030","residual_fossil_MtCO2_2040","residual_fossil_MtCO2_2050"),
  reference_value=c(
    round((df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value))),
    round((df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value))),
    round((df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value)))
  ),
  min = c(
    round((min(df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
    round((min(df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
    round((min(df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value))))
  ),
  max = c(
    round((max(df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
    round((max(df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
    round((max(df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value))))
  )
)

renewablesShare %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

ElectricityShare %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

hydrogenProduction %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

ElectricityDemand %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

SolarPV %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

Wind %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

# Primary Energy
vars <- c("Oil"="PE|Oil",
          "Gas"="PE|Gas",
          "Coal"="PE|Coal",
          "Biomass" = "PE|Biomass")
